Analysis

### 2023-02-05 Analysis.rmd
update code to fetch prediction data from github

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(covid.german.forecasts)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)
library(dplyr)
library(tidyr)
library(forcats)

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = '')
library(here)
library(magrittr)
library(scoringutils)
library(knitr)
library(kableExtra)
library(data.table)
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(patchwork)
library(stringr)
library(grates)
library(ggdist)
library(ggthemes)
library(scales)
library(dplyr)
library(tidyr)
library(forcats)

@@

```{r}
forecasts <- fread("data/forecast-data.csv")
scores <- fread("data/all-scores-crowd-forecasts.csv")
weekly_truth <- fread("data/weekly-truth-Europe.csv")
daily_truth <- fread("data/daily-truth-Europe.csv")

time_start <- as.Date("2021-05-24")
time_stop <- as.Date("2021-08-16")

label_fn <- function(x) {
  x <- ifelse(x%%1 == 0, 
              as.integer(x), x)
  ifelse(x < 1000, 
         paste(x), 
         ifelse(x < 1e6, 
                paste0(x / 1000, "k"),
                ifelse(x < 1e9, 
                       paste0(x / 1e6, "m"), 
                       paste0(x / 1e9, "b"))
         )
  )
}

```{r}
weekly_truth |>
  ggplot(aes(x = target_end_date, y = true_value)) +
  annotate("rect", xmin = time_start, xmax = time_stop, ymin = 0, ymax = Inf,
           fill = "darkolivegreen3", alpha = .1) + 
  geom_line() + 
  geom_point(size = 0.8, aes(color = status)) + 
  geom_bar(data = daily_truth |>
             mutate(true_value = true_value * 7), 
           stat = "identity", 
           fill = "skyblue3", alpha = 0.4) + 
  facet_wrap(~ target_type, 
             nrow = 2, scale = "free_y") + 
  scale_y_continuous(labels = label_fn) +
  theme_scoringutils() + 
  scale_colour_manual(values = c("red", "black")) + 
  labs(y = "Observed value", x = "Date", color = "Data status")
```

```{r}
forecasts |>
  filter(target_end_date >= "2021-04-01", 
         target_end_date <= "2021-10-01") |>
  filter(model == "direct crowd") |>
